## White Wine Quality by Kristin Lynch
========================================================



```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load the packages.

library(ggplot2)
library(knitr)
library(dplyr)
library(GGally)
library(memisc)

```

```{r echo=FALSE,message=FALSE, warning=FALSE, Load_the_Data}
# Load the Data
wine <- read.csv('wineQualityWhites.csv')
```

> The data set analyzed was about the quality of white Portugese wines in 2009. 
There are multiple variables to test how they impact the quality rating of the 
wine.<br> 
Data was from this source:<br>
  P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis. 
  Modeling wine preferences by data mining from physicochemical properties.
  In Decision Support Systems, Elsevier, 47(4):547-553. ISSN: 0167-9236.

# Univariate Plots Section

> This section will show the table dimensions (rows, columns), as well as the 
column names and data types. The first six lines of the data frame 
have been printed. 

```{r echo=FALSE, message=FALSE, warning=FALSE,Univariate_Plots}
# dimensions
dim(wine)

# Show the variables
str(wine)

#Print the first 6 lines.
head(wine)
```

> This section will show a summary of the variables. 
These variables will be explored closer by using graphs, 
but the summary reveals some points of interest to explore more closely. <br>
1) The max for residual sugar compared to the 3rd Quartile reveals that there 
are outliers. <br>
2) The min and max for total sulfur dioxide show the largest range of the 
variables. <br> 
3) The quality scale is from 1 (very bad) to 10 (very excellent), but the range
of values is from 3 to 9. With a median of 6, and a mean of 5.878, 
the wines skewed towards the higher quality. <br> 

```{r echo=FALSE, message=FALSE, warning=FALSE,Wine_Summary}
#summary of the data frame
summary(wine)
```
```{r echo= FALSE, message=FALSE, warning=FALSE,fixed.acidity}
#histogram on fixed acidtiy
ggplot(aes(x = fixed.acidity), data = wine) +
  geom_histogram() 

```

> The fixed acidity of the wine has most values between the six to seven range.
 We can use log to look at this in a different way since it has a long tail. 
 
```{r echo=FALSE, message=FALSE, warning=FALSE,Fixed-Log}
#View with log 10
ggplot(aes(fixed.acidity), data = wine) +
  geom_histogram() +
  scale_x_log10()

```

> By looking at this in log, we can see a more normal distribution.

```{r echo=FALSE ,message=FALSE, warning=FALSE, volatile}
#histogram volatile acidtiy
ggplot(aes(volatile.acidity), data = wine) +
  geom_histogram()
```

>High levels of volatile acidity can lead to an unpleasant taste according to 
the explanation on the data set.I'm wondering if those wines that are rated over
.6 would have lower ratings than the rest of the wines because most wines fell 
under that value and that is well over the third quartile.


```{r echo= FALSE , message=FALSE, warning=FALSE, citric.acid}
#Histogram citric acid
ggplot(aes(citric.acid), data = wine) +
geom_histogram()
```

>Small quantities of citric acid can improve the taste of wine. I wonder if this 
will show in the analysis, and at what point will it stop increasing the quality? 

```{r echo= FALSE,message=FALSE, warning=FALSE, residual_sugar}
#Histogram residual sugar
ggplot(aes(residual.sugar) , data = wine)+
  geom_histogram()
```

>The residual sugar was one of the most interesting variables to me because of 
the outliers. While sweet it normally a desired trait in some foods, 
in wine, it is normally in the range of 1 to 45 grams according to the
information on the data set. I wonder if this has an impact on quality, 
since many people prefer dry wine so it's more about preference and subjective. 


```{r echo= FALSE,message=FALSE, warning=FALSE, sugarBox}
#View with log 10
ggplot(aes(residual.sugar) , data = wine)+
  geom_histogram() +
  scale_x_log10()
```

>Because of the long tail, I used the log 10 to transform this data. 
It shows a bimodal range of sugar, with a drop around 3. 
It's possible this is due to trying to classify wines as dry or sweet and 
three would be hard to classify. 
We will need to look at this closer to see its correlation to quality.

```{r echo = FALSE,message=FALSE, warning=FALSE, Chlorides}
#Histogram cholrides
ggplot(aes(chlorides), data  = wine) +
  geom_histogram() +
  scale_x_continuous(limits = c(0,0.10), breaks = seq(0, 0.1, 0.05))
```

>Chlorides are the salt in wine. While this has a very long tail and could be
looked at in log, for this one I limited the range to .10. The third quartile
starts at .05, the mean is .04 and median is .043. This variable may impact the 
quality, but it would only be for a very small amount.

```{r echo=FALSE,message=FALSE, warning=FALSE, ChlorideSummay}
#Summarize chlorides to explain graph.
summary(wine$chlorides)
```


```{r echo = FALSE, message=FALSE, warning=FALSE,free.sulfur.dioxide}
#Histogram sulfur dioxide
ggplot(aes(x = free.sulfur.dioxide), data = wine) +
  geom_histogram()
```

 >Free sulfur dioxide prevents microbial growth according to the information
 about the data set. If this does impact quality, it would not be intentional 
 like some of the other variables such as sweetness. 
 
```{r echo = FALSE,message=FALSE, warning=FALSE, total.sulfur.dioxide}
#Histogram sulfur dioxide
ggplot(aes(total.sulfur.dioxide), data  = wine)+
  geom_histogram()
```

>Free sulfur dioxide was on the the variables that I was most curious about. 
The outliers are so much futher out of range than the other variables. 
I would like to see this on a box plot later, and would like to investigate if
these were in error. This is added for purpose, not to improve the taste, 
but I wonder what the extreme values do to quality. 

```{r echo = FALSE,message=FALSE, warning=FALSE, sulfur_dectectable}
#Histogram only on detectable levels of sulfur dioxide
df.detectable.Sulfur <- subset(wine, total.sulfur.dioxide >= 50)
ggplot(aes(x = total.sulfur.dioxide), data = df.detectable.Sulfur) +
  geom_histogram() +
  scale_x_log10()
```

>According to the data set, only amounts over 50mg are detectable. I created a new variable for a data frame that only includes the detectable sulfur amounts to use on quality at a later point. I added log to this chart of the values over 50mg to include the long tail.

```{r echo = FALSE ,message=FALSE, warning=FALSE,Density}
# Histogram on density with summary
ggplot(aes(x = density), data = wine) +
  geom_histogram()
summary(wine$density)
```

>The density of the wine is in the same range of water according to the text 
report. Water can change density at different temperatures according to google,
but it is still in this range. I don't see this variable as interesting as the
others as I don't think I have ever noticed a difference in my drinking water. 


```{r echo= FALSE,message=FALSE, warning=FALSE, ph}
#Histogram on pH
ggplot(aes(x = pH), data = wine) +
  geom_histogram()
```

>This graph has a normal distribution. All wines in this study are acidic. They fall between the range of vinegar and tomato juice in similar examples.

```{r echo= FALSE,message=FALSE, warning=FALSE, sulphates}
#Histogram on sulphates
ggplot(aes(x = sulphates), data = wine) +
  geom_histogram()
```

>Sulphates are not added to improve quality, but instead are another variable
that is added for purpose. I am curious about sulphates because it is one of the
components of wine that is frequently mentioned. I wonder if it has an impact? 

```{r echo= FALSE, message=FALSE, warning=FALSE,alcohol}
#Histogram on alcohol
ggplot(aes(alcohol), data = wine) +
  geom_histogram()
```

>Alcohol is one of the variables I am most curious about. There are some
varieties of wine that have more alcohol, like a port which is also very sweet.
While this study is on white wines, I wonder if we will see the sugar content
have a postive correlation with alcohol to balance out the taste. I also wonder 
how this impacts the quality rating.  The median wine is 10.4, and the average 
is 10.51, so the measurements of center are very close.

```{r echo=FALSE,message=FALSE, warning=FALSE, alcoholsummary}
#Summary of Alcohol to explain above graph.
summary(wine$alcohol)
```

```{r echo = FALSE ,message=FALSE, warning=FALSE, Quality}
#Histogram on quality
ggplot(aes(x = quality), data = wine) +
  geom_histogram(binwidth =  1)
```
 
 >The wine quality is evenly distributed. No wines were ranked really poor
 (below 3), and none were ranked really excellent (perfect 10).
 Most were ranked slightly above what would be an average rating of 5. The 
 actual average was 5.78, with a median of 6. I imagine that it would be hard
 to be profitable with a very poor wine, so I'm surprised this isn't skewed 
 even more to the right.
 
```{r echo = FALSE, message=FALSE, warning=FALSE,summary_quality}
#Summary of the wine quality
summary(wine$quality)

```




# Univariate Analysis


### What is the structure of your dataset?
> The data set is 4898 records, 13 columns and in tidy format. 

### What is/are the main feature(s) of interest in your dataset?
> The main features of interest is what variables would make wine rank higher
in quality. After the univariate analysis, the three variables that are the most
interesting to me are the total sulfur dioxide, alcohol and residual sugar and
their impact on quality.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?
> I think some of the variables that don't show a direct correlation to the 
quality will start to show an impact when layered with other variables. 

### Did you create any new variables from existing variables in the dataset?
>I am going to create a categorical ranking from the quality in the next section. I did create a variable for a subset of the data frame for sulfur over 50mg since under that is mentioned that it is not detectable. 

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?
> I adjusted one of the graphs to log because of the long tail. This allowed us
to better see the distribution. 

# Bivariate Plots Section



```{r echo=FALSE, message=FALSE, warning=FALSE,Bivariate_Plots}
#Show the correlation matrix
cor(wine)
```

>Most of the variables do not show a strong correlation with quality, which is 
not that surprising. I originally thought that it would be a combination of 
variables. If one variable had such a strong correlation on quality, we probably
would not see as much of a range, as it would most likely be more of a standard 
amount added (unless cost was a major factor). I was suprised that alcohol had 
the strongest correlation to quality on its own. Another surprise, is the 
correlation with density. I assumed this would be close to 0 but it's actually
stronger than more after alcohol.I'll explore that in another graph.

```{r echo = FALSE,message=FALSE, warning=FALSE, GGPair}
#Remove columns to subset the data frame and show the more interesting variables

wine_subset <- wine[, c(8:13)]

ggpairs((wine_subset),
  columnLabels = c('Ttl SD', 'Density','pH','Sulphates','Alcohol','Quality') )
  ggtitle('Correlation Matrix')



```

>This correlation matrix allows us to see some of the more interesting 
correlations and plots.
The strongest correlation is the negative correlation between density and 
alcohol.We start to see that even in the small scatterplot but we will explore 
that more in another section.

```{r echo = FALSE,message=FALSE, warning=FALSE, correlation_wineAndSugar}

#Test the correlation of wine and sugar
cor.test(wine$alcohol, wine$residual.sugar, data = wine)


```

>I had wanted to see the correlation between alcohol and sugar. I had assumed 
that as the alcohol content went up, more sugar would be added to help balance 
the strong taste. There is actually a negative correlation instead. After 
seeing this graph, it makes more sense that the sugar is left behind by the 
fermentation process, not added for taste.

```{r echo = FALSE, message=FALSE, warning=FALSE,AlcoholvsSugar}
# Scatter plot with alcohol and sugar
ggplot(aes(x = alcohol, y = residual.sugar), data = wine) +
  geom_jitter(alpha = 1/10, position = 'jitter', color = 'blue') +
  geom_smooth(method="lm") +
  xlab('Alcohol Content Percent by Volume') +
  ylab('Residual Sugar in grams') +
  ggtitle('Alcohol and Sugar Content in White Wines')

```


>I was surprised to see the negative correlation between alcohol and sugar 
content. The higher the alcohol, generally the lower the sugar. It's possible
that is because people that typically don't enjoy wine would want something 
lighter and sweeter, like a wine cooler, in addition to the ferementation 
process itself.This does not show causation between the variables, 
only that a negative relationship exists.

```{r echo = FALSE, message=FALSE, warning=FALSE, Create_VAR }

#Make a categorical variable based on ratings.
wine_quality <- wine %>% mutate(quality_cat = case_when(quality < 4 ~ 'Poor', 
                                          quality < 6 & quality >= 4 ~ 'Normal',
                                          quality >= 6 & quality < 8 ~ 'Good', 
                                          quality >= 8  ~ 'Excellent'))

head(wine_quality)
```

>I've added a variable to categorize the wine into buckets based on quality. 
This is based on my own ideas and not listed in the explanation of the data set
. The data set lists 1 as very poor, and 10 as very excellent, but there are no 
values at either of those numbers so those were not included.<br>

>Poor is listed as anything with a rating of less than 4 in this new dataframe.
In this data set, that would only include a rating of 3. Normal is 4 and 5. 
Good is 6 and 7. Anything 8 and over is excellent (The range of this data set
is 3 to 9.)

```{r echo = FALSE, message=FALSE, warning=FALSE, CreateBoxPlot }
#Box plot by Quality Category to show Alcohol percentage
ggplot(aes(x = quality_cat, y = alcohol), data = wine_quality ) +
  geom_boxplot() +
  xlab('Quality of Wine') +
  ylab('Alcohol Percentage by Volume') +
  ggtitle('Alcohol Content by Quality') +
  stat_summary(fun = mean, shape = 4, geom = 'point')
```

>This is interesting, because excellent quality wines clearly have a higher 
average and range of alcohol percentage by volume than the other categories. 
Good has the largest range of values, but is still more alcohol on average than 
normal and poor wines. In the normal category, wines have a lower alcohol 
content on average than the good, but there is a string of outliers that have a 
very high content. Finally, Poor does have more alcohol on average than normal.

```{r echo= FALSE, dectable_sulfur}
#Graph with only detectable levels of sulfur.
ggplot(aes(y = total.sulfur.dioxide, x = quality),data = df.detectable.Sulfur) +
  geom_point() +
  scale_x_continuous(breaks = seq(1,10,1)) +
  xlab('Quality') +
  ylab('Sulfur Dioxide- Total mg') +
  geom_smooth(method= 'lm')+
  ggtitle('Detectable Free Sulfur and Quality of Wine')

```
>In this plot, I limited the data to detectable sulfur, which according to the
text was over 50 mg.Once we limit it to detectable values we can see there is a
negative correlation between the quality and amount of total sulfur. 
We can see that the outliers with large amounts of sulfur dioxide are rated 
very low (3), while the highest rating of 9 generally has low amounts. 
We can't say that total sulfur dioxide causes the ratings to decrease 
without an experiment. 

```{r echo = FALSE ,message=FALSE, warning=FALSE, citricAcid}

#Subset the data to only include excellent wines
ggplot(aes(y = alcohol, x = residual.sugar), 
       data = subset(wine, quality >= 8)) +
  geom_line( position = 'jitter', color = 'red') + 
  xlab('Residual Sugar in Grams') +
  ylab('Alcohol percentage of Volume') +
  ggtitle('Alcohol and Sugar Content in Excellent Wines')

excellent_wine <- subset(wine, quality >= 8)
```

>This plot subsets the wine table to look at alcohol and sugar content only on
excellent wines (8 or above).
Below, this shows there are 180 records and the mean alcohol is a little higher 
while the mean sugar is a littler lower. The sugar max is only 14 for excellent
wines. 

```{r echo = FALSE, message=FALSE, warning=FALSE, excellentSugar}

# Find the number of records in the subset of Excellent wine. Compare averages.
print('Records & Columns in Excellent Wine Data Frame:')
dim(excellent_wine) 
print('Mean & Median of Residual Sugar Content of All Wines:')
mean(wine$residual.sugar)
median(wine$residual.sugar)

print('Summary of Residual Sugar of Excellent Only')
summary(excellent_wine$residual.sugar)

```



```{r echo = FALSE, message=FALSE, warning=FALSE, densityQualityCat}
#Graphs of Density by Quality
qplot(data = wine_quality, x = density) +
  scale_x_continuous(limits = c(.98,1.03), breaks = seq(.98,1.03,0.01)) +
  facet_wrap(~quality_cat, scales = 'free') +
  xlab('Density in Grams') +
  ylab('Count') +
  ggtitle('Density by Quality')


summary(wine_quality$density)
cor.test(wine_quality$density, wine_quality$quality)
```

>Although it was not strong, there was a negative correlation between the quality 
and density. In this graph, by the categories, it appears most appear in the same 
range. We will have to explore this in more detail in the multivariate plots. 

```{r echo = FALSE, message=FALSE, warning=FALSE,SulphatePoly}
#Frequency Polygon
#Make it a proportionate frequency polygon:
ggplot(aes(x = sulphates),
       data = wine_quality) +
  geom_bar(aes(color = quality_cat), binwidth = 10) +
  scale_x_continuous(limits = c(0.1, 1.2), breaks = seq(0.1, 1.3, .1)) +
  xlab('Sulphates in Grams') +
  ylab('Count') +
  ggtitle('Sulphates- Frequency of Grams by Quality')

summary(wine$sulphates)
```

>The median for sulphates is .47 across all groups. Because it is not added to 
enhance the quality, I didn't expect
it to have an impact on quality. However, because it is one of the variables 
that I often hear mentioned, I wanted to see if it did have an impact.
From this graph, it is likely that sulphates do not have an impact on quality.




# Bivariate Analysis


### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?
> In this section, I observed that the strongest correlation on quality was 
alcohol. There was also a negative correlation between the total sulfur and 
quality, once only the detectable sulfur was observed.

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?
>There was a negative correlation between sugar and alcohol. This is especially 
intersting since there is a direct correlation between alcohol and quality. 


### What was the strongest relationship you found?
> The strongest relationship was the correlation of alcohol to quality. 

# Multivariate Plots Section



```{r echo=FALSE, message=FALSE, warning=FALSE,Multivariate_Plots}
#Scatterpot for Alcohol and Sugar
ggplot(aes(x = alcohol, y = residual.sugar, color = quality_cat), 
         data = wine_quality) + 
  geom_point(alpha = 0.75, size = 2, position = 'jitter') +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title ='Quality Category',reverse = T,
                                    override.aes = list(alpha = 1, size = 2))) +  
  scale_x_continuous( limits = c(8, 14),
                     breaks = seq(8, 14, 1)) + 
  scale_y_continuous( limits = c(0, 40),
                     breaks = seq(0, 40, 5)) +
  ggtitle('Quality by Alcohol Content and Residual Sugar')
```

>The excellent wines tend to have more alcohol and less sugar. The alcohol is 
more of a factor than the sugar.

```{r echo = FALSE, message=FALSE, warning=FALSE, sulfurD}
#Line graph sulphate, sulfure dioxide by Quality
ggplot(aes(x = sulphates, y =total.sulfur.dioxide), data = wine_quality) +
  geom_line(aes(color= quality_cat), stat = 'summary',
            fun = mean) +
  scale_color_brewer(palette = 'Dark2') +
  geom_line(stat = 'summary', fun = mean, linetype = 2) +
  xlab('Sulphates') +
  ylab('Total Sulfur Dioxide') +
  ggtitle('Quality Category by Sulphates and Total Sulfur Dioxide')

#Correlation for variables on graph.
cor.test(wine_quality$sulphates, wine_quality$total.sulfur.dioxide)
```

>There is an extremely weak positive correlation between total sulfur dioxide and 
sulphates. Both are not added to enhance quality, but only to keep the wine safe
to drink and preserve it. According to this chart, we can't see any impact on
the quality from sulphates, but we can see that any of the total sulfur well 
over the averages tends to be rated poor.

```{r echo = FALSE,message=FALSE, warning=FALSE, DensitySugarAlcohol}
#Scatterplot to show relationship between density, sugar and alchohol
ggplot(aes(x = density, y = residual.sugar, color = alcohol), data = wine) + 
  geom_point(alpha = 0.75, size = 2, position = 'jitter') +
  scale_x_continuous( limits = c(0.99, 1.01),
                     breaks = seq(0.99, 1.01, .01)) + 
  scale_y_continuous( limits = c(0, 25),
                     breaks = seq(0, 25, 5)) +
  ggtitle('Alcohol Content by Residual Sugar and Density')
```

>In the original analysis, the density seemed that such a small range (equivalent
to the range of water) would be hard to detect. However, it did show some 
correlation to the other variables. This plot limits the range to take out the 
outliers. This shows that as the density and sugar increases, 
the alcohol content tends to decrease.

```{r echo= FALSE, message=FALSE, warning=FALSE, Model}
#Setting up the models. 
# We are looking for high r squared values.This model is based on density. 

q1 <- lm(I(density) ~ I(alcohol), data = wine)
q2 <- update(q1, ~ . + residual.sugar)
q3 <- update(q1, ~ . + pH)
q4 <- update(q2, ~ . + sulphates)

mtable(q1, q2, q3, q4)

```

>Despite the correlation of alcohol and quality, I was unable to create a model
that was strong enough to predict quality based on alcohol. 
However, the R-value is very strong for predicting density, based on alcohol
and residual sugar, and even stronger if sulphates are added. 

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?
It takes sugar to make alcohol, so it did not surprise me that there was a 
relationship there. It surprised me that R value was not strong when those
were used. There was a relationship between density, residual sugar and alcohol.


### Were there any interesting or surprising interactions between features?
I was very surprised to see that the density when combined with alcohol seemed
to impact the quality. The density range was so small and equivalent to the 
range of water at different temperatures, so I didn't think that would be 
detectable. 

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.
I was unable to find a model to predict the quality. I am curious about the data
set. Price is missing, so I think that these features should be checked in 
a similar price range (all wines about $20), or price should be included. 


------

# Final Plots and Summary



### Plot One
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_One}
#Plot to show alcohol content by quality
ggplot(aes(x = quality_cat, y = alcohol), data = wine_quality ) +
  geom_boxplot(fill = topo.colors(4)) +
  xlab('Quality of Wine') +
  ylab('Alcohol Percentage by Volume') +
  ggtitle('Alcohol Content by Quality') +
  stat_summary(fun = mean, shape = 4, geom = 'point')
```

### Description One
>This box plot shows the quality of wine and percentage of Alcohol by Volume. 
The median increases across normal, good and excellent wines. Poor wines have 
more alcohol by mean and median than normal wines. The average also increases
at normal and up. The normal quality group has the most outliers. 
This information could be used to create another model excluding poor quality
to predict quality by alcohol content.

### Plot Two
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Two}
#Graph on alcohol and sugar and quality
ggplot(aes(x = alcohol, y = residual.sugar, color = quality_cat), 
       data = wine_quality) + 
  geom_point(alpha = 0.95, size = 1, position = 'jitter') +
  scale_color_brewer(type = 'div',
                     guide = guide_legend(title = 'Quality Category',
                                          reverse = T,
                                          override.aes = list(alpha = 1, 
                                                              size = 1))) +  
  scale_x_continuous( limits = c(8, 14),
                     breaks = seq(8, 14, 1)) + 
  scale_y_continuous( limits = c(0, 40),
                     breaks = seq(0, 40, 5)) +
  geom_smooth(method ='lm') +
  xlab('Alcohol (Percentage by Volume)') +
  ylab('Residual Sugar (grams)') +
  ggtitle('Quality by Alcohol Content and Residual Sugar')
```

### Description Two
>This graph shows the relationship between sugar and alcohol and how they were 
rated by category. Breaking the wines into groups by rating, helps to 
show that as the alcohol increases, the sugar tends to decrease and the rating
tends to increase. While this seems to happen in most categories, the poor
category doesn't react to these variables like the other categories. 

### Plot Three
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Three}
#Graph on alcohol, sugar, density
ggplot(aes(x = density, y = residual.sugar, color = alcohol), data = wine) + 
  geom_point(alpha = 0.75, size = 2, position = 'jitter') +
  scale_x_continuous( limits = c(0.99, 1.01),
                     breaks = seq(0.99, 1.01, .01)) + 
  scale_y_continuous( limits = c(0, 25),
                     breaks = seq(0, 25, 5)) +

  xlab('Density (grams)')+
  ylab('Residual Sugar (grams)') +
  ggtitle('Alcohol (Percentage by Volume) by Residual Sugar and Density')
```

### Description Three
>This graph shows the relationship between alcohol, sugar and density. These were
the strongest of the correlations that I found between variables.
As the density and sugar increase, the alcohol decreases. 

------

# Reflection


>In this analysis, the strongest relationships I found were from sugar, alcohol 
and density. I expected sugar and alcohol to have a correlation with quality, 
but I was surprised it wasn't stronger. It was unexpected that density would
be related. There were some variables like total sulfuric dioxide that should
not have impacted the taste of the wine but did show changes related to quality
in the detectable range.<br>
I think this data range should either contain wines of the same price range, 
or it should include the price. While amounts of variables were measured, 
quality of the grapes or ingredients were not. I would suspect an $800 bottle 
of wine would rate much higher than a $10 bottle with similar sugar, alcohol 
and density amounts but it is not possible to tell with this analysis.
This data set could be used create an algorithm for people to answer a few 
questions on preferences and then create a suggestion list. It could be used
by a grocery store to feature certain wines that would rate higher with more 
consumers.

### Sites Used:
<br>
https://stackoverflow.com/questions/21560389/non-numeric-argument-to-binary-operator <br>
https://community.rstudio.com/t/creating-a-new-variable-under-conditions-of-other-two-variables/51825 <br>
https://www.py4u.net/discuss/868741 <br>
https://statisticsbyjim.com/regression/interpret-r-squared-regression/ <br>
